Deep Neural Networks for Bilingual Lexicon Extraction

### 2014-07-15 paper/main.tex
added Arthur contributions

>>>>

\section{Contributions}
\label{sec:contributions}

Jon developed the translation framework in Python, building off several existing tools (notably Word2Vec, Gensim, and Pylearn). He trained a suite of models and evaluated them on manually sourced translation seeds.

Arthur also applied this method to translate from the King James Bible
to a modern English translation. The results there were not so
interesting as they mostly mapped the same words onto themselves. He
also wrote a tool to map the vector spaces in t-SNE, but this is still
a work in progress.
